---
title: "Final Project - Website Analytics"
author: "Sakshi Shende"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# import necessary libraries
library(stringr)
library(ggplot2)
library(gridExtra)
#install.packages("vctrs")
library(tidyr)
library(tibble)
library(lubridate)
library(plyr)
library(dplyr)
library(tidyverse)
library(xts)
library(forecast)
library(tseries)
library(corrplot)
library(stats)
#install.packages("vars")
library(vars)
#install.packages("MTS")
library(MTS)
#install.packages("prophet")
library(prophet)
library(xts)
```

```{r}
# import the data
df = read.csv('train_1.csv')
head(df)

# get the data shape
dim(df)
```

# Data Processing

### Rename the columns

```{r}
# get the column names
col_names = colnames(df)

# Remove leading "X" from column names
col_names = gsub("^X", "", col_names)

# Replace "." with "-"
col_names = gsub("\\.", "-", col_names)

#rename the column names
colnames(df) = col_names

head(df)
```

### Extract specific name, language, access_type and access origin

```{r}
# Extract specific name, language, access type, and access origin
pattern = "^(.*?)_([a-z]{2})\\.wikipedia\\.org_([^_]+)_([^_]+)$"
matches = str_match(df$Page, pattern)

# Create a data frame with the extracted values
extracted_data = data.frame(
  specific_name = matches[, 2],
  language = matches[, 3],
  access_type = matches[, 4],
  access_origin = matches[, 5]
)

# Assign the extracted values to the original dataframe
df$specific_name = extracted_data$specific_name
df$language = extracted_data$language
df$access_type = extracted_data$access_type
df$access_origin = extracted_data$access_origin

head(df)
```

### Handle missing data

```{r}
unique(df$language)

# check for missing values
sum(is.na(df))/(ncol(df)*nrow(df))*100


print('Shape before removing missing values:')
dim(df)

# drop the rows with missing values in language data
df = df[!is.na(df$language), ]

print('Shape after removing missing values:')
dim(df)

# replace "" with 0
df[is.na(df)] = 0

head(df)
```

### Data Preparation for Analysis

```{r}
# remove columns not necessary for the analysis
df_prep = subset(df, select = -c(Page, specific_name, access_type, access_origin))

# group views by language
df_prep = aggregate(. ~ language, data = df_prep, FUN = sum)

# scale down the values by 1M and transpose
df_prep[, -1] = df_prep[, -1] / 1000000
df_prep = t(df_prep)

# Rename the column names and remove the first row
colnames(df_prep) = unlist(df_prep[1, ])
data = df_prep[-1, ]

# Convert matrix to data frame
data = as.data.frame(data)

# Convert variables to numeric
data$de = as.numeric(data$de)
data$en = as.numeric(data$en)
data$es = as.numeric(data$es)
data$fr = as.numeric(data$fr)
data$ja = as.numeric(data$ja)
data$ru = as.numeric(data$ru)
data$zh = as.numeric(data$zh)

head(data)
```

### Convert to time series data

```{r}
# Convert the index to a column named 'date'
data = data %>% rownames_to_column(var = "date")

# Convert the 'date' column to a Date object
data$date = as.Date(data$date)

# Create an xts object
xts_data = xts(data[, -1], order.by = data$date)
head(xts_data)

# create a ts object
ts_data_2 = ts(data, start = min(data$date), frequency = 7)
#head(ts_data_2)
```

# Exploratory Data Analysis

```{r}
p1 = df %>% 
  ggplot(aes(access_origin)) + geom_bar(fill = "red")
p2 = df %>% 
  ggplot(aes(access_type)) + geom_bar(fill = "red")
p3 = df %>% 
  ggplot(aes(language, fill = language)) + geom_bar() + theme(legend.position = "none")

grid.arrange(p1, p2, p3)
```

```{r}
plot1 = ggplot(data, aes(x = de)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

plot2 = ggplot(data, aes(x = en)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

plot3 = ggplot(data, aes(x = es)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

plot4 = ggplot(data, aes(x = fr)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

plot5 = ggplot(data, aes(x = ja)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

plot6 = ggplot(data, aes(x = ru)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

plot7 = ggplot(data, aes(x = zh)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), bins = 10, color = "black", fill = "lightblue") +
  geom_density(color = "red") +
  labs(y = "Percent")

grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, plot7)
```

```{r}
# Create the boxplot
boxplot(data[c('de', 'en', 'es', 'fr', 'ja', 'ru', 'zh')], horizontal = TRUE, xlab = 'Views on the page')

# Add a title
title(main = 'Views on the page')
```

### Time Series Plot

```{r}
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = de)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for German language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
# 
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = en)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for English language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
# 
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = es)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for Spanish language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
# 
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = fr)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for French language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
# 
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = ja)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for Japanese language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
# 
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = ru)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for Russian language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
# 
# ggplot(data = data, aes(x = as.Date(rownames(data)), y = zh)) +
#   geom_line(color = "blue") +
#   geom_point(shape = "*") +
#   labs(title = "Total page view for Chinese language", x = "Date", y = "Page Views") +
#   theme_minimal() +
#   scale_x_date(date_labels = "%b %Y", date_breaks = "2 months")
```

```{r}
plot(xts_data, main = "Time Series Plot")



# Assuming your xts time series object is named 'xts_data'
library(ggplot2)

# Assuming your xts time series object is named 'xts_data'

# Convert the xts object to a data frame
df <- as.data.frame(xts_data)

# Add the date column from the index of the xts object to the data frame
df$date <- index(xts_data)

# Reshape the data from wide to long format
df_long <- tidyr::pivot_longer(df, cols = -date, names_to = "Language", values_to = "Value")

# Plotting the graph
ggplot(df_long, aes(x = date, y = Value, color = Language)) +
  geom_line(size = 1) +
  labs(title = "Pages in Different Languages", y = "Views per page") +
  theme_minimal() +
  theme(legend.position = "top")


```

### Seasonal Decomposition

```{r}
# Perform seasonal decomposition for each column
for (col in colnames(ts_data_2)) {
  decomposed <- stl(ts_data_2[, col], s.window = "periodic", robust = TRUE)
  
  # Access the components
  trend <- decomposed$time.series[, "trend"]
  seasonal <- decomposed$time.series[, "seasonal"]
  residual <- decomposed$time.series[, "remainder"]
  
  # Plot the components
  plot(decomposed, main = paste("Seasonal Decomposition -", col))
}


```

### Stationarity

```{r}
for (col in colnames(xts_data)) {
  adf_test = adf.test(xts_data[, col])
  cat("\n ADF test for column:", col, "\n")
  print(adf_test)
  
  if (adf_test$p.value < 0.05) {
    cat("The time series is stationary\n")
  } else {
    cat("The time series is non-stationary\n")
  }
}
```

```{r}
print('Autocorrelation for German Language')
par(mfrow=c(1,2))
acf(xts_data[,1], main = 'Autocorrelation for German Language')
pacf(xts_data[,1], main = 'Autocorrelation for German Language')

print('Autocorrelation for English Language')
par(mfrow=c(1,2))
acf(xts_data[,2], main = 'Autocorrelation for English Language')
pacf(xts_data[,2], main = 'Autocorrelation for English Language')

print('Autocorrelation for Spanish Language')
par(mfrow=c(1,2))
acf(xts_data[,3], main = 'Autocorrelation for Spanish Language')
pacf(xts_data[,3], main = 'Autocorrelation for Spanish Language')

print('Autocorrelation for French Language')
par(mfrow=c(1,2))
acf(xts_data[,4], main = 'Autocorrelation for French Language')
pacf(xts_data[,4], main = 'Autocorrelation for French Language')

print('Autocorrelation for Japanese Language')
par(mfrow=c(1,2))
acf(xts_data[,5], main = 'Autocorrelation for Japanese Language')
pacf(xts_data[,5], main = 'Autocorrelation for Japanese Language')

print('Autocorrelation for Russian Language')
par(mfrow=c(1,2))
acf(xts_data[,6], main = 'Autocorrelation for Russian Language')
pacf(xts_data[,6], main = 'Autocorrelation for Russian Language')

print('Autocorrelation for Chinese Language')
par(mfrow=c(1,2))
acf(xts_data[,7], main = 'Autocorrelation for Chinese Language')
pacf(xts_data[,7], main = 'Autocorrelation for Chinese Language')
```

We can see that the some of the time-sreis are non-stationary, to handle this, we'll us auto-arima to perform differencing.

### Differencing

```{r}
head(xts_data)

stationary_vars = c(2, 4, 6, 7)
differenced_vars = c(1, 2, 3, 4, 5, 6, 7)

# apply differencing to non-stationary variables
diff_data = diff(xts_data[,differenced_vars], differences = 1)

# Combine stationary and differenced variables
# diff_xts_data = cbind(xts_data[, stationary_vars], diff_data)
# head(diff_xts_data)

diff_xts_data = diff_data
head(diff_xts_data)
```

```{r}
diff_xts_data[is.na(diff_xts_data)] = 0

for (col in colnames(diff_xts_data)) {
  adf_test <- adf.test(diff_xts_data[, col])
  cat("\n ADF test for column:", col, "\n")
  print(adf_test)
  
  if (adf_test$p.value < 0.05) {
    cat("The time series is stationary\n")
  } else {
    cat("The time series is non-stationary\n")
  }
}
```

### Autocorrelation

```{r}
print('Autocorrelation for German Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,1], main = 'Autocorrelation for German Language')
pacf(diff_xts_data[,1])

print('Autocorrelation for English Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,2], main = 'Autocorrelation for English Language')
pacf(diff_xts_data[,2])

print('Autocorrelation for Spanish Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,3], main = 'Autocorrelation for Spanish Language')
pacf(diff_xts_data[,3])

print('Autocorrelation for French Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,4], main = 'Autocorrelation for French Language')
pacf(diff_xts_data[,4])

print('Autocorrelation for Japanese Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,5], main = 'Autocorrelation for Japanese Language')
pacf(diff_xts_data[,5])

print('Autocorrelation for Russian Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,6], main = 'Autocorrelation for Russian Language')
pacf(diff_xts_data[,6])

print('Autocorrelation for Chinese Language')
par(mfrow=c(1,2))
acf(diff_xts_data[,7], main = 'Autocorrelation for Chinese Language')
pacf(diff_xts_data[,7])
```

### Descriptive Statistics

```{r}
summary(diff_xts_data)
corrplot(cor(diff_xts_data))
```

### Moving Average Smoothing

```{r}
ma_smooth = ma(diff_xts_data, order = 3)
plot(ma_smooth, main = "Moving Average Smoothed")
```

# Modelling

### Train/test Split

```{r}
train_data = diff_xts_data['/2016-12-16']
dim(train_data)
test_data = diff_xts_data['2016-12-17/']
dim(test_data)

plot(train_data[,1])
plot(test_data[,1])


# train_data = xts_data['/2016-12-16']
# dim(train_data)
# test_data = xts_data['2016-12-17/']
# dim(test_data)
```

### ARIMA

```{r}
# fit arima model
arima = auto.arima(train_data[,1], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)
# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values, main = 'de')

# Extract actual and forecasted values
actual = test_data[, 1]
forecasted = forecast_values$mean

# Calculate MAPE
mape_de = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = de, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- de" )) +
    theme_minimal()
```

```{r}
# fit arima model
arima = auto.arima(train_data[,2], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)
# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values)

# Extract actual and forecasted values
actual = test_data[, 2]
forecasted = forecast_values$mean

# Calculate MAPE
mape_en = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = en, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- en" )) +
    theme_minimal()
```

```{r}
# fit arima model
arima = auto.arima(train_data[,3], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)
# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values)

# Extract actual and forecasted values
actual = test_data[, 3]
forecasted = forecast_values$mean

# Calculate MAPE
mape_es = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = es, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- es" )) +
    theme_minimal()
```

```{r}
# fit arima model
arima = auto.arima(train_data[,4], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)
# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values)

# Extract actual and forecasted values
actual = test_data[, 4]
forecasted = forecast_values$mean

# Calculate MAPE
mape_fr = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = fr, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- fr" )) +
    theme_minimal()
```

```{r}
# fit arima model
arima = auto.arima(train_data[,5], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)
# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values)

# Extract actual and forecasted values
actual = test_data[, 5]
forecasted = forecast_values$mean

# Calculate MAPE
mape_ja = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = ja, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- ja" )) +
    theme_minimal()
```

```{r}
# fit arima model
arima = auto.arima(train_data[,6], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)
# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values)

# Extract actual and forecasted values
actual = test_data[, 6]
forecasted = forecast_values$mean

# Calculate MAPE
mape_ru = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = ru, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- ru" )) +
    theme_minimal()
```

```{r}
# fit arima model
arima = auto.arima(train_data[,7], stepwise = FALSE, approximation = FALSE)
summary(arima)
checkresiduals(arima)

# Forecast h steps ahead
forecast_values = forecast(arima, h = 15)
plot(forecast_values)

# Extract actual and forecasted values
actual = test_data[, 7]
forecasted = forecast_values$mean

# Calculate MAPE
mape_zh = mean(abs((actual - forecasted) / actual))

# Create a data frame with actual and forecasted values
df = data.frame(Time = index(actual), Actual = actual, Predicted = forecasted)

# Plot using ggplot
ggplot(df, aes(x = Time)) +
    geom_line(aes(y = zh, color = "Actual")) +
    geom_line(aes(y = Predicted, color = "Predicted")) +
    scale_color_manual(values = c("Actual" = "blue", "Predicted" = "red")) +
    labs(x = "Time", y = "Value", title = paste("Actual vs. Predicted- zh" )) +
    theme_minimal()
```

### SARIMAX

```{r}
sarimax_en = Arima(train_data$en, order=c(5, 0, 0), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_en)
checkresiduals(sarimax_en)

# Make predictions
predictions <- forecast(sarimax_en, h = length(test_data$en))

# Calculate MAPE
actual <- test_data$en
predicted <- predictions$mean

mape_en_x <- mean(abs((actual - predicted) / actual))

title <- "English Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$en),
  actual = test_data$en,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), linewidth = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

```{r}
sarimax_de = Arima(train_data$de, order=c(1, 0, 0), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_de)
checkresiduals(sarimax_de)

# Make predictions
predictions <- forecast(sarimax_de, h = length(test_data$de))

# Calculate MAPE
actual <- test_data$de
predicted <- predictions$mean

mape_de_x <- mean(abs((actual - predicted) / actual))

title <- "German Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$de),
  actual = test_data$de,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

```{r}
sarimax_es = Arima(train_data$es, order=c(1, 0, 0), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_es)
checkresiduals(sarimax_es)

# Make predictions
predictions <- forecast(sarimax_es, h = length(test_data$es))

# Calculate MAPE
actual <- test_data$es
predicted <- predictions$mean

mape_es_x <- mean(abs((actual - predicted) / actual))

title <- "Spanish Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$es),
  actual = test_data$es,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

```{r}
sarimax_ja = Arima(train_data$ja, order=c(4, 0, 1), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_ja)
checkresiduals(sarimax_ja)

# Make predictions
predictions <- forecast(sarimax_ja, h = length(test_data$ja))

# Calculate MAPE
actual <- test_data$ja
predicted <- predictions$mean

mape_ja_x <- mean(abs((actual - predicted) / actual))

title <- "Japanese Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$ja),
  actual = test_data$ja,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

```{r}
sarimax_ru = Arima(train_data$ru, order=c(2, 0, 3), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_ru)
checkresiduals(sarimax_ru)
# Make predictions
predictions <- forecast(sarimax_ru, h = length(test_data$ru))

# Calculate MAPE
actual <- test_data$ru
predicted <- predictions$mean

mape_ru_x <- mean(abs((actual - predicted) / actual))

title <- "Russian Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$ru),
  actual = test_data$ru,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

```{r}
sarimax_zh = Arima(train_data$zh, order=c(5, 0, 0), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_zh)
checkresiduals(sarimax_zh)

# Make predictions
predictions <- forecast(sarimax_zh, h = length(test_data$zh))

# Calculate MAPE
actual <- test_data$zh
predicted <- predictions$mean

mape_zh_x <- mean(abs((actual - predicted) / actual))

title <- "Chinese Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$zh),
  actual = test_data$zh,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

```{r}
sarimax_fr = Arima(train_data$fr, order=c(1, 1, 1), seasonal=list(order=c(1, 0, 1), period=7))
summary(sarimax_fr)
checkresiduals(sarimax_fr)

# Make predictions
predictions <- forecast(sarimax_fr, h = length(test_data$en))

# Calculate MAPE
actual <- test_data$fr
predicted <- predictions$mean

mape_fr_x <- mean(abs((actual - predicted) / actual))

title <- "French Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test_data$fr),
  actual = test_data$fr,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")
```

### SARIMAX with EXOG

```{r}
exog = read.csv('Exog_Campaign_eng')
dim(exog)

df_exog = xts_data
df_exog$exog = exog$Exog
head(df_exog)


train = df_exog['/2016-12-16']
dim(train)
test= df_exog['2016-12-17/']
dim(test)
```

```{r}
sarima_en = Arima(train$en, order=c(5, 0, 0), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_en)


checkresiduals(sarima_en)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_en, h = length(test$en), xreg = exog_forecast)


# Calculate MAPE
actual <- test$en
predicted <- predictions$mean

mapex_en <- mean(abs((actual - predicted) / actual))

title <- "English Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$en),
  actual = test$en,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

```{r}
sarima_de = Arima(train$de, order=c(2, 0, 3), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_de)
checkresiduals(sarima_de)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_de, h = length(test$de), xreg = exog_forecast)


# Calculate MAPE
actual <- test$de
predicted <- predictions$mean

mapex_de <- mean(abs((actual - predicted) / actual))


title <- "German Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$de),
  actual = test$de,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

```{r}
sarima_es = Arima(train$es, order=c(5, 0, 0), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_es)
checkresiduals(sarima_es)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_es, h = length(test$es), xreg = exog_forecast)


# Calculate MAPE
actual <- test$es
predicted <- predictions$mean

mapex_es <- mean(abs((actual - predicted) / actual))


title <- "Spanish Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$es),
  actual = test$es,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

```{r}
sarima_fr = Arima(train$fr, order=c(3, 0, 1), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_fr)
checkresiduals(sarima_fr)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_fr, h = length(test$fr), xreg = exog_forecast)


# Calculate MAPE
actual <- test$fr
predicted <- predictions$mean

mapex_fr <- mean(abs((actual - predicted) / actual))


title <- "french Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$fr),
  actual = test$fr,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

```{r}
sarima_ja = Arima(train$ja, order=c(4, 0, 1), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_ja)
checkresiduals(sarima_ja)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_ja, h = length(test$ja), xreg = exog_forecast)


# Calculate MAPE
actual <- test$ja
predicted <- predictions$mean

mapex_ja <- mean(abs((actual - predicted) / actual))


title <- "Japanese Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$ja),
  actual = test$ja,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

```{r}
sarima_zh = Arima(train$zh, order=c(5, 0, 0), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_zh)
checkresiduals(sarima_zh)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_zh, h = length(test$zh), xreg = exog_forecast)


# Calculate MAPE
actual <- test$zh
predicted <- predictions$mean

mapex_zh <- mean(abs((actual - predicted) / actual))


title <- "french Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$zh),
  actual = test$zh,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

```{r}
sarima_ru = Arima(train$ru, order=c(2, 0, 3), seasonal=list(order=c(1, 0, 1), period=7), xreg=train$exog)
summary(sarima_ru)
checkresiduals(sarima_ru)

start <- length(train) + 1
end <- length(train) + length(test) - 1

# Prepare exogenous variables for forecasting
exog_forecast <- test$exog

# Make predictions
predictions <- forecast(sarima_ru, h = length(test$ru), xreg = exog_forecast)


# Calculate MAPE
actual <- test$ru
predicted <- predictions$mean

mapex_ru <- mean(abs((actual - predicted) / actual))


title <- "french Language Page views Actual vs Predicted"
ylabel <- "Page views"
xlabel <- ""

# Create a data frame with actual and predicted values
plot_data <- data.frame(
  index = seq_along(test$ru),
  actual = test$ru,
  predicted = predictions$mean
)

# Plot actual vs predicted values using ggplot
ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = actual, color = "Actual"), size = 1) +
  geom_line(aes(y = predicted, color = "Predicted"), size = 1) +
  scale_color_manual(values = c("Actual" = "blue", "Predicted" = "orange")) +
  labs(title = title, x = xlabel, y = ylabel) +
  theme_minimal() +
  theme(legend.position = "top")

# Add vertical lines for exogenous events
for (i in which(test$exog == 1)) {
  geom_vline(xintercept = i, linetype = "dashed", color = "red")
}
```

# Model Evaluation

```{r}
model_eval = data.frame(model = c("ARIMA", "SARIMA", "SARIMAX with Exog"),
                       DE = c(mape_de, mape_de_x, mapex_de),
                       EN = c(mape_en, mape_en_x, mapex_en),
                       ES = c(mape_es, mape_es_x, mapex_es),
                       FR = c(mape_fr, mape_fr_x, mapex_fr),
                       JA = c(mape_ja, mape_ja_x, mapex_ja),
                       RU = c(mape_ru, mape_ru_x, mapex_ru),
                       ZH = c(mape_zh, mape_zh_x, mapex_zh))
model_eval
```

```{r}
ggplot(model_eval, aes(x = model, y = DE, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for DE") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplot(model_eval, aes(x = model, y = EN, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for EN") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplot(model_eval, aes(x = model, y = ES, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for ES") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplot(model_eval, aes(x = model, y = FR, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for FR") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplot(model_eval, aes(x = model, y = JA, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for JA") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplot(model_eval, aes(x = model, y = RU, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for RU") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplot(model_eval, aes(x = model, y = ZH, fill = model)) +
  geom_col(position = "dodge") +
  labs(x = "Model", y = "MAPE", title = "Model Evaluation for ZH") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
